A Survey Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
304 > 305; added in coding agreement statistics.

After participants answered the two comprehension questions, participants were presented with 6 randomly selected questions from a set of 304 questions on various scenarios which can occur when wearing the Cubetastic3000. Out of these 304 questions, 292 (73 <data> * 4 <recipient>) were questions of the format: \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.

@@

\subsection{Analysis}
After removing 465 incomplete responses, our sample consisted of 1,785 participants. Of these X, A\% were male, with a median age of B. For the wearables and smartphone questions, we use the very upset rate (VUR) of various scenarios, rather than taking an average of the participants' upset ratings (after assigning each rating a number) from the likert scale. The VUR also does not presume that the ratings, ranging from indifferent to very upset, are linearly spaced. Additionally, we believe that everyone would be upset at least a little bit at the given scenarios, in which an device takes action without permission. Therefore, we believe that the main distinguishing factor of a participant reacting to a given situation is if they are maximally upset or not, rather than how upset they were. Although participants gave a wide range of numbers (i.e. a participant who answered that one technology was six orders of magnitude more beneficial than another), we do not normalize the numerical responses for the risk/benefit analysis. Rather, we use values such as the median, and various quartiles for our analysis which are not heavily impacted by outliers. Two researchers independently coded 1,785 open-ended responses, discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.

>>>>

After participants answered the two comprehension questions, participants were presented with 6 randomly selected questions from a set of 305 questions on various scenarios which can occur when wearing the Cubetastic3000. Out of these 305 questions, 292 (73 <data> * 4 <recipient>) were questions of the format: \textit{``How would you feel if an app on your Cubetastic3000 learned <data> and shared it with <recipient>, without asking you first?''}.

@@

\subsection{Analysis}
After removing 465 incomplete responses, our sample consisted of 1,785 participants. Of these X, A\% were male, with a median age of B. For the wearables and smartphone questions, we use the very upset rate (VUR) of various scenarios, rather than taking an average of the participants' upset ratings (after assigning each rating a number) from the likert scale. The VUR also does not presume that the ratings, ranging from indifferent to very upset, are linearly spaced. Additionally, we believe that everyone would be upset at least a little bit at the given scenarios, in which an device takes action without permission. Therefore, we believe that the main distinguishing factor of a participant reacting to a given situation is if they are maximally upset or not, rather than how upset they were. Although participants gave a wide range of numbers (i.e. a participant who answered that one technology was six orders of magnitude more beneficial than another), we do not normalize the numerical responses for the risk/benefit analysis. Rather, we use values such as the median, and various quartiles for our analysis which are not heavily impacted by outliers. Two researchers independently coded 1,785 open-ended responses and had an initial agreement rate of 89.78\%. The researchers discussed any disagreements, and resolved them so that the final codings reflect unanimous agreement.
